---
title: "STA457H1F Assignment 1"
author: 
- "Ahmed Nawaz Amanullah, St.# 1001325773"
- "Ling Long, St.# ####"
date: "February 24, 2019"
output: pdf_document
---

# Part A
## Question 1
In this section, we will find the optimal double moving average (MA) trading rules for all 30 DJ constituents using monthly data.  As hinted by the assignment, we will refer to the Fall 2018 assignment to implement this.  We will proceed in chronological order of said assignment in order to gain understanding of this question.  

We will predict the direction of the trend of asset prices using a function of past asset prices $F_t$, which will be converted to buy and sell trading signals $B_t$, with buy corresponding to +1 and sell to -1.  $F_t$ will be based on a moving-average technical indicator, which can be expressed as a function of log returns:

$$F_t = \delta + \sum_{j = 0}^{m-2}d_jX_{t-j}$$

where $X_t = ln(P_t/P_{t-1})$, while $\delta$ and $d_j$ are defined by a given trading rule.  For the assignment, we will assume $\delta = 0$.

The function is then, as mentioned earlier, converted to trading signals as follows:

$$\left\{ 
      \begin{array}{ll}
      "Sell" \iff B_t = -1 \iff F_t < 0\\
      "Buy" \iff B_t = +1 \iff F_t > 0
      \end{array}
    \right.
$$

We will also be assessing the results and performance of trading decisions, and the returns at time $t$ will be obtained using "ruled returns", which will be denoted as $R_t$.  So if for a period $[t-1, t)$, a trader establishes a  position at time $t-1$, represented by $B_{t-1}$, the "ruled returns" expression is as follows:

$$R_t = B_{t-1}X_t \iff \left\{
                            \begin{array}{ll}
                            R_t = -X_t & \quad  B_{t-1} = -1\\
                            R_t = +X_t & \quad  B_{t-1} = +1
                            \end{array}
                          \right.
$$

where $X_t = ln(P_t/P_{t-1})$ denote the logarithm return over this period (so we will be assuming no dividend payouts during the time period).

The realized returns will thus be determined using:
$$\tilde{R_t} = \sum_{D = 1}^{n}R_{t + D}$$

where $D$ represents the stochastic duration of the position lasting $n$ days provided that:

$$\left\{D = n\right\} \iff \left\{B_{t-1} \neq B_t, B_t = ... = B_{t+n-1}, B_{t+n-1} \neq B_{t+n}\right\}$$

###Step 1: Derive variance of predictor $F_t$
The variance of the predictor is derived as follows:

$$\sigma_F^2 = var(\sum_{i = 0}^{m-2} d_i X_{t-i})$$
$$= cov(\sum_{i = 0}^{m-2} d_iX_{t-i}, \sum_{i = 0}^{m-2}d_iX_{t-i})$$
$$= d_0cov(X_t, \sum_{i = 0}^{m-2}d_iX_{t-i}) + d_1cov(X_{t-1}, \sum_{i = 0}^{m-2}d_iX_{t-i}) + ... + d_{m-2}cov(X_{t-m+2}, \sum_{i = 0}^{m-2}d_iX_{t-i})$$
$$= d_0(d_0\gamma_0 + d_1\gamma_1 + ... + d_{m-2}\gamma_{m-2}) + d_1(d_0\gamma_1 + d_1\gamma_0 + d_2\gamma_1 + ... + d_{m-2}\gamma_{m-3}) + ... + d_{m-2}(d_0\gamma_{m-2} + d_1\gamma_{m-3} + ... + d_{m-2}\gamma_0)$$
$$= \gamma_0 \sum_{i = 0}^{m-2}d_i^2  + 2\sum_{i = 1}^{m-2} \sum_{j = 0}^{m-2-i}d_jd_{j+i}\gamma_i$$
$$= \gamma_0 (\sum_{i = 0}^{m-2}d_i^2  + 2\sum_{i = 1}^{m-2} \sum_{j = 0}^{m-2-i}d_jd_{j+i}\rho_i)$$
$$= \gamma_0 (\sum_{i = 0}^{m-2}d_i^2  + 2\sum_{j = 0}^{m-2} \sum_{i = j+1}^{m-3}d_jd_{i}\rho_{i-j})$$

Provided below is the R code for computing the variance of the predictor:

```{r results = "hide"}
#Step 1: Get the variance of the predictor
# d: vector of dj coefficients (j = 0, ..., m-2)
# X: log returns
#Will use quadratic form... 
varF <- function(d, X){
	#maximum lag
	M <- length(d)-1
	#get auto-covariance
	acfs <- acf(X, plot = F, type="covariance", lag.max=M)$acf
	#get toeplitz matrix of acfs
	#name used to refer to:
	#[[\gamma_0, ..., \gamma_{m-2}],
	# [\gamma_1, \gamma_0, ..., \gamma_{m-3}], ...
	# [\gamma_{m-2}, ..., \gamma_0]]
	Gamma <- toeplitz(as.vector(acfs))
	#quadratic form
	varF <- d%*%Gamma%*%as.vector(d)
	varF
}

```

Note that the implementation above uses the quadratic form of the expression:

$$\sigma_F^2 =
\left[\begin{array}{ccc}
        d_0 & ... & d_{m-2}
        \end{array}\right]
\left[\begin{array}{ccc}
        \gamma_0 & ... & \gamma_{m-2}\\
        ... & ... & ...\\
        \gamma_{m-2} & ... & \gamma_{0}
        \end{array}\right]
\left[\begin{array}{c}
        d_0\\
        ...\\
        d_{m-2}
      \end{array}\right]
$$

###Step 2: Derive expectation of predictor $F_t$
The expectation of the predictor is derived as follows:

$$\mu_F = E(\sum_{i=0}^{m-2} d_iX_{t-i})$$
$$= \sum_{i=0}^{m-2} d_iE(X_{t-i})$$
$$= \mu_X\sum_{i=0}^{m-2} d_i$$

Provided below is the R code for computing the expectation of the predictor:

```{r results = "hide"}
#Step 2: Get the expectation of the predictor
# d: vector of dj coefficients (j = 0, ..., m-2)
# X: log returns
muF <- function(d, X){
	muF <- mean(X)*sum(d)
	muF
}

```

###Step 3: Derive autocorrelation function at lag one for predictor
The expression for the autocorrelation function for lag 1 is derived as follows:

$$\rho_F(1) = corr(F_t, F_{t - 1}) = \frac{cov(F_t, F_{t - 1})}{var(F_t)}$$

First the covariance expression,

$$cov(F_t, F_{t - 1})= corr(\sum_{i=0}^{m-2} d_iX_{t-i}, \sum_{i=0}^{m-2} d_iX_{t-1-i})$$
$$= d_0cov(X_t, \sum_{i=0}^{m-2} d_iX_{t-1-i}) + d_1cov(X_{t-1}, \sum_{i=0}^{m-2} d_iX_{t-1-i}) + ... + d_{m-2}cov(X_{t-m+2}, \sum_{i=0}^{m-2} d_iX_{t-1-i})$$
$$= d_0(d_0\gamma_1 + d_1\gamma_2 + ... + d_{m-2}\gamma_{m-1}) + d_1(d_0\gamma_0 + d_1\gamma_1 + d_2\gamma_2 + ... + d_{m-2}\gamma_{m-2}) + ... + d_{m-2}(d_0\gamma_{m-3} + d_1\gamma_{m-4} + ... + d_{m-2}\gamma_1)$$
$$= \gamma_0\left\{ d_0(d_0\rho_1 + d_1\rho_2 + ... + d_{m-2}\rho_{m-1}) +  ... + d_{m-2}(d_0\rho_{m-3} + d_1\rho_{m-4} + ... + d_{m-2}\rho_1) \right\}$$
$$= \gamma_0\sum_{i = 0}^{m-2}\sum_{j = 0}^{m-2}d_id_j\rho_{j - 1 - i}$$

Then the autocorrelation function:

$$\rho_F(1) = \frac{cov(F_t, F_{t - 1})}{var(F_t)}$$
$$= \frac{\gamma_0\sum_{i = 0}^{m-2}\sum_{j = 0}^{m-2}d_id_j\rho_{j - 1 - i}}{var(F_t)}$$

Provided below is the R code for computing the lag one autocorrelation of the predictor:

```{r results = "hide"}
#Step 3: Computing ACF(1) of forecaster
#will use a quadratic form
# d: vector of dj coefficients (j = 0, ..., m-2)
# X: log returns
rhoF <- function(d, X){
	#max lag
	M <- length(d)-1
	#get acfs
	acfs <- acf(X, plot = F, type = "covariance", lag.max = M+2)$acf
	#get the covariance
	temp <- d%*%matrix(acfs[as.vector(
	abs(outer(0:M,1:(M+1), "-"))+1)], M+1, M+1)%*%as.vector(d)
	rhoF <- temp/varF(d, X)
	rhoF
}
```

Additionally note that as with when computing the variance of the predictor, a similar approach utilizing matrix multiplication is being used above:

$$cov(F_t, F_{t-1}) =
\left[\begin{array}{ccc}
        d_0 & ... & d_{m-2}
        \end{array}\right]
\left[\begin{array}{cccc}
        \gamma_1 & ... & ... &\gamma_{m-1}\\
        ... & ... & ...& ...\\
        ... & ... & ...& ...\\
        \gamma_{m-3} & ... & \gamma_0 & \gamma_1
        \end{array}\right]
\left[\begin{array}{c}
        d_0\\
        ...\\
        d_{m-2}
      \end{array}\right]
$$

###Step 4: Computing the expected ruled returns and expected holding period length

Under the assumption that $X_t$ follows a stationary Gaussian process, the expected ruled returns has been provided as follows:

$$E(R_t) = \sqrt{\frac{2}{\pi}}\sigma_Xcorr(X_t,F_{t-1})exp\left\{-\frac{\mu_F^2}{2\sigma_F^2}\right\} + \mu_X(1 - 2\phi\left[ -\frac{\mu_F}{\sigma_F} \right])$$

Most of the expressions needed for this computation has been derived earlier.  We just need the expression:

$$corr(X_t,F_{t-1}) = \frac{cov(X_t,F_{t-1})}{\sqrt{\gamma_0var(F_t)}}$$
$$= \frac{(d_0\gamma_1 + d_1\gamma_2 + ... + d_{m-2}\gamma_{m-1})}{\sqrt{\gamma_0var(F_t)}}$$
$$= \frac{\gamma_0\sum_{i=0}^{m-2}d_i\rho_{i+1}}{\sqrt{\gamma_0var(F_t)}}$$

The R code for implementing this computation is as follows:

```{r results = "hide"}
#Step 4 Intermediate: correlation between X_t and F_{t-1}
#will use a quadratic form
# d: vector of dj coefficients (j = 0, ..., m-2)
# X: log returns

corXF <- function(d, X){
	Mp <- length(d)
	acfs <- acf(X, plot = F, type = "covariance", lag.max = Mp)$acf
	corXF <- sum(d*acfs[-1])/sqrt(acfs[1]*varF(d, X))
	corXF
}
```

Additionally, the unconditional variance of the ruled returns has been provided as:

$$var(R_t) = E(X_t^2) - E(R_t)^2 = \sigma_X^2 + \mu_X^2 - E(R_t)^2$$

Furthermore, as provided, Kedem (1986) shows that the expected zero-crossing rate for a discrete-time, zero-mean, stationary Gaussian sequence $Z_t$ is given by:

$$\frac{1}{\pi}cos^{-1}\rho_Z(1)$$

where $\rho_Z(1)$ denotes the autocorrelation function of $\left\{Z_t\right\}$ at lag one.  Using this result, we may approximate the expected length of the holding period to be:

$$H = \frac{\pi}{cos^{-1}\rho_F(1)}$$

Provided below is the R code for the computation of the expected holding period, the double MA co-efficients and the expected ruled returns:

```{r results = "hide"}
#Step 4: Expected holding period and ruled returns
#expected holding period
#rho is lag one autocorrelation
#provided by step 3
Hold <- function(rho){
	Hold <- pi/acos(rho)
}

#next is the double MA co-efficients
d <- function(m, r){
	d <- c((m-r)*((0:(r-1))+1), r*(m-(r: (m-1))-1))
	d
}

# retX: log asset return
# m: long-term MA
# r: short-term MA

ruleReturn <- function(retX, m, r){
	#returns variance
	vX <- sd(retX)
	#returns mean
	mX <- mean(retX)
	#predictor mean
	mF <- muF(d(m, r), retX)
	#predictor sd
	vF <- sqrt(varF(d(m, r), retX))
	#lag 1 correlation (rho) between X_t and F_{t-1}
	rXF <- corXF(d(m, r), retX)
	#lag 1 correlation of predictor
	rF <- rhoF(d(m, r), retX)
	#expected return
	ER <- sqrt(2/pi)*vX*rXF*exp(-mF*mF/(vF*vF)) + 
	mX*(1-2*pnorm(-mF/vF))
	#expected hold duration
	H <- Hold(rF)
	#return results
	list("ER" = ER, "H" = H, "rhoF" = rF, "VF"= vF, "muF"=mF, 
	"corXF"=rXF)
}

```

###Step 5: Downloading the monthly data of the constituents
The data for the DJ constituents were downloaded from Yahoo Finance in csv files and stored in a folder.  The R code for retrieving this data from the csv files is as follows:

```{r results = "hide"}
#This function is to download data from folder...
#idea: return three arrays - one containing the stock tickers...
#	another the adjusted close (using hint from prev assn) 
#	and finally one containing the log returns

# dataDir: directory containing csv files containing data
# currDir: current working directory (to change back to after 
#	loading data)
getAdC <- function(dataDir, currDir){
	#switch to directory containing price data
	setwd(dataDir)
	#get list of files in directory
	priceFiles <- list.files(dataDir, pattern="*.csv", 
	full.names = F, recursive = F)
	#to hold tickers
	tickers <- c()
	#to hold prices
	prices <- c()
	#to hold log returns
	logrets <- c()
	#iterate through list above
	for (file in seq(1, length(priceFiles))){
		tickers <- c(tickers, substr(priceFiles[file],
		1,nchar(priceFiles[file])-4))
		#use rbind for the adjusted close data...
		#first read the file
		stockdat <- read.csv(file = priceFiles[file],
		 header = T, sep=",")
		#then get adjusted close prices from file
		price <- stockdat[1:dim(stockdat)[1], 6] 
		prices <- rbind(prices, price)
		#also the log returns
		logrets <- rbind(logrets, 
		log(price[2:length(price)]/price[1:(length(price)-1)]))
	}
	#return to original directory
	setwd(currDir)
	
	#return tickers, prices and log returns
	list("tickers"=tickers, "prices"=prices, "logrets" = logrets)
}

```

###Step 6: Writing R function to find optimal monthly double MA trading rules
Provided below are the R functions utilized to find the optimal double MA trading rules using monthly data:

```{r results = "hide"}
#Function to choose the optimal daily and monthly MA trading rules
#	(i.e. that maximize expected rule returns)
#will test function against the one in prev assn after 
#	implementation...

#first optimal monthly
#	retX: vector of log returns
monthlyoptimal_dma <- function(retX){
	#to hold optimal m and r
	optimal_m <- 2
	optimal_r <- 1
	#get ruleReturn for this setting
	currER <- ruleReturn(retX, optimal_m, optimal_r)$ER
	#iterate up to 12 max as we are doing monthly
	#loop through r
	for (i in seq(1, 11)){
		for (j in seq(i+1, 12)){
			ERij <- ruleReturn(retX, j, i)$ER
			if (ERij > currER){
				optimal_m <- j
				optimal_r <- i
				currER <- ERij
			} 
		}
	}
	#return optimal double MA trading rules
	list("monthlyoptimal_m"=optimal_m, "monthlyoptimal_r"=optimal_r)
}

#functions that will implement the above for all constituents...

#	retsX: the log returns of the constituents 

monthlyoptimals_dma <- function(retsX){
	#to hold the optimal trading rules
	m <- c()
	r <- c()
	#amount of tickers to go through
	numstocks <- dim(retsX)[1]
	#number of periods/ months
	months <- dim(retsX)[2]
	for (i in seq(1, numstocks)){
		optimals <- monthlyoptimal_dma(retsX[i, 1:months])
		#add optimals to list
		m <- c(m, optimals$monthlyoptimal_m)
		r <- c(r, optimals$monthlyoptimal_r)
	} 
	
	#return optimal rules
	list("monthlyoptimals_m"=m, "monthlyoptimals_r"=r)
}
```

Disclosed below are the optimal trading rules found for the constituents:

```{r, echo=FALSE}
dataDir <- "/Users/amanull9/Documents/STA457/Assignments/STA457-Assn1/Assn 1/DJ Data Monthly"
currDir <- "/Users/amanull9/Documents/STA457/Assignments/STA457-Assn1/Assn 1"

monthlydata <- getAdC(dataDir, currDir)
tickers <- monthlydata$tickers
mprices <- monthlydata$prices
mlogrets <- monthlydata$logrets

#get optimals for all 30 constituents
dj_optimals <- monthlyoptimals_dma(mlogrets)

#construct table
djoptimals_table <- t(rbind(tickers, dj_optimals$monthlyoptimals_m,dj_optimals$monthlyoptimals_r))

#column names
colnames(djoptimals_table)[2:3] <- c("m", "r")

#kable
library(knitr)
kable(djoptimals_table, caption = "DJ double MA optimal trading rules")

```

###Step 7: Writing R function to compute in-sample trading statistics and compare with theoretical results

Please find below the functions implemented in R to generate the in-sample as well as theoretical trade statistics (cumulative return and holding time) for the optimal trade rules derived earlier.

```{r results = "hide"}
#functions for computing in-sample trading statistics 
#	(i.e. cumulative return and holding time)
#	to later compare with theoretical results
#first function to compute the predictor

#	d: d is d(m ,r) - presumably the optimal ones found
#	retX: the log returns
#	t: get signal at time t

f <- function(d, retX, t){
	M <- length(d) - 1
	if (t >= M){
		output <- sum(d*rev(retX[(t-M):t]))
		output
	}
	else {print('t is smaller than M')}
}

#next the realized return
#	d: d is d(m ,r) - presumably the optimal ones found
#	retX: the log returns
realized_ret <- function(d, retX){
	re <- c()
	M <- length(d)
	for (t in seq(M + 1,length(retX))){
		re <- c(re, sign(f(d, retX, t-1))*retX[t])
	}
	realized_ret <- sum(re)/length(M:length(retX))
	realized_ret
}

#next is the holding period
holding_period <- function(d, retX){
	num_change <- 0
	M <- length(d)
	for (t in seq(M+1, length(retX))){
		if (sign(f(d, retX,t)) != sign(f(d, retX,t-1))){
			num_change <- num_change + 1
		}
	}
	hold <- length(M:length(retX))/num_change
	hold
}

#function that will take in the array of log returns 
#	and the optimal trading decisions
in_sample_estimate <- function(retX, m, r){
	#number of tickers
	num_stocks <- dim(retX)[1]
	#number of periods/ months
	#to hold in_sample and theoretical values
	djER <- c()
	djH <- c()
	djISR <- c()
	djISH <- c()
	months <- dim(retX)[2]
	for (i in seq(1, num_stocks)){
		ruleReturn_i <- ruleReturn(retX[i, 1:months], m[i], r[i])
		djER <- c(djER, ruleReturn_i$ER)
		djH <- c(djH, ruleReturn_i$H)
		djISR <- c(djISR, 
		realized_ret(d(m[i],r[i]),retX[i, 1:months]))
		djISH <- c(djISH, 
		holding_period(d(m[i],r[i]),retX[i, 1:months]))
	}
	#return estimated and theoretical values 
	list("djER"=djER ,"djH"=djH, "djISR"=djISR, "djISH"=djISH)
}

```

The results are disclosed below as well:
```{r, echo=FALSE}
dj_tradestats <- in_sample_estimate(mlogrets,dj_optimals$monthlyoptimals_m,dj_optimals$monthlyoptimals_r)

#Ok outputting something which is good

#code for having this in a table
dj_tradestats_table <- t(rbind(tickers, round(dj_tradestats$djER,4),  round(dj_tradestats$djISR,4), round(dj_tradestats$djH,3), round(dj_tradestats$djISH,3)))

colnames(dj_tradestats_table)[2:5] <- c("theoretical return",  "expected return","theoretical hold", "expected hold")

#kable
kable(dj_tradestats_table, caption = "DJ double MA optimal trading rules statistics")

```

## Question 2
In this section, we will construct the equally weighted (EW) and risk-parity (RP) weighted portfolios using the 30 DJ constituents and summarize the performance.  

As per general instruction, performance will be based on a 60-month rolling window and the portfolio will be rebalanced monthly.  The parameters ($\sigma$) will be calibrated/ estimated at the end of each year.

The following assumptions are going to be made:

  1. Will use the 60-month window to get optimal trading rules.
  
  2. Will use these optimal settings to predict the signals for next month
  
  3. For risk parity, will use the last 12 months of window to calibrate the asset volatilities (see section B) as brought up earlier.
  
  4. Use predicted signal and portfolio weights to get rule return of portfolio (see hint).
  
  5. Check performance of next 12 months using predicted signals.    Since we recalibrate parameters annually (i.e. at end of each year), we will re-calculate the ex-ante volatilities every 12 months.
  
  6. The 60-month window moves 12 months ahead and we repeat (1-5).  Process terminates when we reach the end of our data.
  
Please find the implementation of these steps for the equally weighted portfolio as follows:

```{r, echo = FALSE}
ea_volatility <- function(retX){
	#need to solve for delta
	#according to paper delta has been solved for as
	delta <- 0.2
	#number of stocks
	num_stocks <- dim(retX)[1]
	#number of periods provided
	t <- dim(retX)[2]
	#vector to hold the ex ante volatilities
	ea_sd <- c()
	#need to iterate over the stocks
	for (s in seq(1, num_stocks)){
		#compute the exponentially weighted returns
		r_bar <- sum((1-delta)*(delta^c(0:11))*
		rev(retX[s, (t-12):(t-1)]))
		#next the ex-ante volatility (annualized)
		#first the variance
		var <- 12*sum((1-delta)*(delta^c(0:11))*
		(rev(retX[s, (t-12):(t-1)])-r_bar)^2)
		#then add the ex-ante volatility of stock s to list
		ea_sd <- c(ea_sd, sqrt(var))
	}
	
	#return volatilities
	ea_sd
} 
```

```{r results = "hide"}
#Question 2: summarizing performance of the equally weighted
#	portfolio
#	retX: 30X(periods) dim matrix of monthly log returns

ew_performance <- function(retX){
	#number of stocks provided
	num_stocks <- dim(retX)[1]
	#number of periods of data provided
	months <- dim(retX)[2]
	#to hold the ruled returns
	re <- c()
	#to hold the cumulative return up to time t
	cre <- c()
	#to hold expected return at time t
	ere <- c()
	#to hold the ex-ante volatility at time t
	ea_sd <- c()
	#to hold sharpe ratio at time t
	sharpes <- c()
	#only go up to as long as window can be fit
	for (i in seq(1, months - 60, 12)){
		#get optimal dma within 60 month window for all stocks
		optimal_dma <- monthlyoptimals_dma(
		retX[1:num_stocks, i:(i+60-1)])
		m <- optimal_dma$monthlyoptimals_m
		r <- optimal_dma$monthlyoptimals_r
		#need to get the ex-ante volatility every 12 months
		ea_sd_i <- ea_volatility(
		retX[1:num_stocks,1:(i+60-1)])
		#Ok, now we use the optimal trading rules to find the 
		#	ruled return for each stock
		#to hold portfolio weights
		#this is an ew portfolio so all weights are the same
		weights <- rep(1/num_stocks, num_stocks)
		
		#this is the portfolio variance
		var_t <- 0
		for (s in seq(1, num_stocks)){
			var_t <- var_t + (weights[s]^2)*ea_sd_i[s]^2
		}
		
		ea_sd <- c(ea_sd, sqrt(var_t))
		
		#going back to old method
		for (t in seq(i + 60, i + 72 -1)){
			if (t <= months){
				re_t <- 0
				for (s in seq(1, num_stocks)){
					s_d <- d(m[s], r[s])
					re_t <- re_t + weights[s]*
					sign(f(s_d, retX[s, 1:months], t-1))*retX[s,t]
				}
				#now add the portfolio ruled return
				re <- c(re, re_t)
				if (length(re) > 1){
					cre <- c(cre, cre[length(cre)] + re_t)
				}else{
					cre <- c(cre, re_t)
				}
				#expected (annual) return at time t
				ere <- c(ere, (12*cre[length(cre)]/length(cre)))
				#as well the sharpe
				sharpe_t <- (ere[length(ere)]-0.02)/
				ea_sd[length(ea_sd)]
				sharpes <- c(sharpes, sharpe_t)
				#note that since this is a EW portfolio, there is 
				#	no rebalancing step as weights remain the same 
			}
		}
		
		
	}
	
	#return results
	list("return"=ere[length(ere)], 
	"volatility"=ea_sd[length(ea_sd)], 
	"sharpe"=sharpes[length(sharpes)], "cumul_return"=cre, 
	"e_return"=ere, "ea_volatilities"=ea_sd, "sharpes"=sharpes)
}

#risk parity function
rp_performance <- function(retX){
	#number of stocks provided
	num_stocks <- dim(retX)[1]
	#number of periods of data provided
	months <- dim(retX)[2]
	#to hold the ruled returns
	re <- c()
	#to hold the cumulative return up to time t
	cre <- c()
	#to hold expected return at time t
	ere <- c()
	#to hold the ex-ante volatility at time t
	ea_sd <- c()
	#to hold sharpe ratio at time t
	sharpes <- c()
	#only go up to as long as window can be fit
	for (i in seq(1, months - 60, 12)){
		#get optimal dma within 60 month window for all stocks
		optimal_dma <- monthlyoptimals_dma(
		retX[1:num_stocks, i:(i+60-1)])
		m <- optimal_dma$monthlyoptimals_m
		r <- optimal_dma$monthlyoptimals_r
		#need to get the ex-ante volatility every 12 months
		ea_sd_i <- ea_volatility(
		retX[1:num_stocks,1:(i+60-1)])
		#Ok, now we use the optimal trading rules to find the 
		#	ruled return for each stock
		#to hold portfolio weights
		#this is an ew portfolio so all weights are the same
		temp <- 1/ea_sd_i
		weights <- temp/sum(temp)
		
		#this is the portfolio variance
		var_t <- 0
		for (s in seq(1, num_stocks)){
			var_t <- var_t + (weights[s]^2)*ea_sd_i[s]^2
		}
		
		ea_sd <- c(ea_sd, sqrt(var_t))
		
		#going back to old method
		for (t in seq(i + 60, i + 72 -1)){
			if (t <= months){
				re_t <- 0
				for (s in seq(1, num_stocks)){
					s_d <- d(m[s], r[s])
					re_t <- re_t + weights[s]*
					sign(f(s_d, retX[s, 1:months], t-1))*retX[s,t]
				}
				#now add the portfolio ruled return
				re <- c(re, re_t)
				if (length(re) > 1){
					cre <- c(cre, cre[length(cre)] + re_t)
				}else{
					cre <- c(cre, re_t)
				}
				#expected (annual) return at time t
				ere <- c(ere, (12*cre[length(cre)]/length(cre)))
				#as well the sharpe
				sharpe_t <- (ere[length(ere)]-0.02)/
				ea_sd[length(ea_sd)]
				sharpes <- c(sharpes, sharpe_t)
				#note that since this is a EW portfolio, there is 
				#	no rebalancing step as weights remain the same 
			}
		}
		
		
	}
	
	#return results
	list("return"=ere[length(ere)], 
	"volatility"=ea_sd[length(ea_sd)], 
	"sharpe"=sharpes[length(sharpes)], "cumul_return"=cre, 
	"e_return"=ere, "ea_volatilities"=ea_sd, "sharpes"=sharpes)
}

```

The performance results obtained implementing the function above is as follows:


```{r, echo=FALSE, fig.width = 7, fig.height = 7}
dj_ew_performance <- ew_performance(mlogrets)

#code for having this in a table
dj_ew_performance_table <- t(rbind(round(dj_ew_performance$return,4),  round(dj_ew_performance$volatility,4), round(dj_ew_performance$sharpe,4)))

colnames(dj_ew_performance_table)[1:3] <- c("Annualized expected return",  "Annualized volatility","Annualized sharpe ratio")

#kinda slow but at least have an output...
#also performance does not seem good, am I doing something wrong?

#hmm - check for risk parity and see if it is still bad
dj_rp_performance <- rp_performance(mlogrets)

#code for having this in a table
dj_rp_performance_table <- t(rbind(round(dj_rp_performance$return,4),  round(dj_rp_performance$volatility,4), round(dj_rp_performance$sharpe,4)))

colnames(dj_rp_performance_table)[1:3] <- c("Annualized expected return",  "Annualized volatility","Annualized sharpe ratio")

#code for plots...
par(mfrow = c(2,2))
plot(c(61:dim(mlogrets)[2]), dj_ew_performance$cumul_return, main = "cumulative log returns", type ="l", xlab = "month", ylab="cumulative return", ylim = c(-0.10, 0.30))
lines(c(61:dim(mlogrets)[2]), dj_rp_performance$cumul_return, col="blue")
plot(c(61:dim(mlogrets)[2]), dj_ew_performance$e_return, main = "annualized expected returns", type = 'l', xlab = "month", ylab="annualized expected return")
lines(c(61:dim(mlogrets)[2]), dj_rp_performance$e_return, col="blue")
plot(seq(61,dim(mlogrets)[2],12), dj_ew_performance$ea_volatilities, main = "annualized ex ante volatilities", type = 'l', xlab = "month", ylab="annualized ex ante volatility", ylim = c(0, 0.04))
lines(seq(61,dim(mlogrets)[2],12), dj_rp_performance$ea_volatilities, col="blue")
plot(c(61:dim(mlogrets)[2]), dj_ew_performance$sharpes, main = "sharpe ratio", type = 'l', xlab = "month", ylab="sharpe ratio", ylim = c(-7, 6))
lines(c(61:dim(mlogrets)[2]), dj_rp_performance$sharpes, col="blue")

#kable
kable(dj_ew_performance_table, caption = "EW performance metrics")
kable(dj_rp_performance_table, caption = "RP performance metrics")
```

# Part B
## Question 1
In this section, we will cover the computation of the ex-ante volatility estimate $\sigma_t$ for the DJ constituents.  The formula used is:

$$\sigma_{s,t}^2 = 12\sum_{i = 0}^{11}(1-\delta)\delta^i(r_{s,t-1-i}-\bar{r}_{s,t})^2$$

Where the weights $\delta^i(1-\delta)$ add up to one, and $\bar{r}_{s,t}$ is the exponentially weighted average return computed similarly:

$$\bar{r}_{s,t} = \sum_{i = 0}^{11}(1-\delta)\delta^ir_{s,t-1-i}$$

For this assignment, as instructed, we will use $\delta = 0.2$. 

The code for implementing this computation in R is as follows:

```{r results = "hide"}
ea_volatility <- function(retX){
	#need to solve for delta
	#according to paper delta has been solved for as
	delta <- 0.2
	#number of stocks
	num_stocks <- dim(retX)[1]
	#number of periods provided
	t <- dim(retX)[2]
	#vector to hold the ex ante volatilities
	ea_sd <- c()
	#need to iterate over the stocks
	for (s in seq(1, num_stocks)){
		#compute the exponentially weighted returns
		r_bar <- sum((1-delta)*(delta^c(0:11))*
		rev(retX[s, (t-12):(t-1)]))
		#next the ex-ante volatility (annualized)
		#first the variance
		var <- 12*sum((1-delta)*(delta^c(0:11))*
		(rev(retX[s, (t-12):(t-1)])-r_bar)^2)
		#then add the ex-ante volatility of stock s to list
		ea_sd <- c(ea_sd, sqrt(var))
	}
	
	#return volatilities
	ea_sd
} 
```

#Part C
## Question 1
In this section, we will make it so that our position to the trading rule is determined by the magnitude of the signal. First, we will need to compute the expected *h*-period holding period return. We have been provided the technical indicator $F_t$:

$$F_t = \sum_{i = 0}^{m - 2}d_ir_{t - i}$$

As well as the *h*-period holding return expression:

$$R_{t:t+h}=\sum_{j=0}^{h-1}F_{t+j}r_{t+j+1}=\sum_{j=0}^{h-1}\left(\sum_{i = 0}^{m - 2}d_ir_{t + j - i}\right)r_{t+j+1}$$

The expected *h*-period holding period return is computed as follows:

$$E(R_{t:t+h}) = E\left(\sum_{j=0}^{h-1}\left(\sum_{i = 0}^{m - 2}d_ir_{t + j - i}\right)r_{t+j+1}\right)$$
$$= E(r_{t+1}(d_0r_{t} + d_1r_{t-1} + ... + d_{m-2}r_{t-m+2}) + ... + r_{t+h}(d_0r_{t+h-1} + ... + d_{m-2}r_{t+h-m+1}))$$
$$= d_0(h\gamma_1) + d_1(h\gamma_2) + ... + d_{m-2}(h\gamma_{m-1})$$
$$= h\sum_{i = 0}^{m-2}d_i\gamma_{i+1}$$

The R-code for the computation of the expected *h*-period holding period return is as follows:

```{r results = "hide"}
e_hperiod_holdperiodreturn <- function(retX, m, r, h){
	#get auto-covariances
	acfs <- acf(retX, plot = F, type = "covariance", lag.max = m)$acf
	#get expected holding period return
	ehphpr <- h*sum(d(m,r)*acfs[2:length(acfs)])
	#return value
	ehphpr
}
```

## Question 2
In this section we will find the optimal double MA for all 30 DJ constituents that maximize the 12-period holding period return.  Please find enclosed below the R-function that was written to implement this:

```{r results = "hide"}
#Ques 2: optimal double MA for 30 DJ constituents maximizing 
#	12-period holding period return.
monthlyoptimalEHR_dma <- function(retX){
	#to hold optimal m and r
	optimal_m <- 2
	optimal_r <- 1
	#get ruleReturn for this setting
	currEHR <- e_hperiod_holdperiodreturn(retX, 
	optimal_m, optimal_r, 12)
	#iterate up to 12 max as we are doing monthly
	#loop through r
	for (i in seq(1, 11)){
		for (j in seq(i+1, 12)){
			EHRij <- e_hperiod_holdperiodreturn(retX, 
			j, i, 12)
			if (EHRij > currEHR){
				optimal_m <- j
				optimal_r <- i
				currEHR <- EHRij
			} 
		}
	}
	#return optimal double MA trading rules
	list("monthlyoptimal_m"=optimal_m, "monthlyoptimal_r"=optimal_r)
}

monthlyoptimalsEHR_dma <- function(retsX){
	#to hold the optimal trading rules
	m <- c()
	r <- c()
	#amount of tickers to go through
	numstocks <- dim(retsX)[1]
	#number of periods/ months
	months <- dim(retsX)[2]
	for (i in seq(1, numstocks)){
		optimals <- monthlyoptimalEHR_dma(retsX[i, 1:months])
		#add optimals to list
		m <- c(m, optimals$monthlyoptimal_m)
		r <- c(r, optimals$monthlyoptimal_r)
	} 
	
	#return optimal rules
	list("monthlyoptimals_m"=m, "monthlyoptimals_r"=r)
}
```

```{r, echo=FALSE}
#get optimals for all 30 constituents
dj_optimalsEHR <- monthlyoptimalsEHR_dma(mlogrets)

#construct table
djoptimalsEHR_table <- t(rbind(tickers, dj_optimalsEHR$monthlyoptimals_m,dj_optimalsEHR$monthlyoptimals_r))

#column names
colnames(djoptimalsEHR_table)[2:3] <- c("m", "r")

#kable
kable(djoptimalsEHR_table, caption = "DJ double MA trading rules for optimal expected 12-period holding period return")

```
