---
title: "STA457H1F Assignment 1"
author: 
- "Ahmed Nawaz Amanullah, St.# 1001325773"
- "Ling Long, St.# ####"
date: "February 24, 2019"
output: pdf_document
---

# Part A
## Question 1
In this section, we will find the optimal double moving average (MA) trading rules for all 30 DJ constituents using monthly data.  As hinted by the assignment, we will refer to the Fall 2018 assignment to implement this.  We will proceed in chronological order of said assignment in order to gain understanding of this question.  

We will predict the direction of the trend of asset prices using a function of past asset prices $F_t$, which will be converted to buy and sell trading signals $B_t$, with buy corresponding to +1 and sell to -1.  $F_t$ will be based on a moving-average technical indicator, which can be expressed as a function of log returns:

$$F_t = \delta + \sum_{j = 0}^{m-2}d_jX_{t-j}$$

where $X_t = ln(P_t/P_{t-1})$, while $\delta$ and $d_j$ are defined by a given trading rule.  For the assignment, we will assume $\delta = 0$.

The function is then, as mentioned earlier, converted to trading signals as follows:

$$\left\{ 
      \begin{array}{ll}
      "Sell" \iff B_t = -1 \iff F_t < 0\\
      "Buy" \iff B_t = +1 \iff F_t > 0
      \end{array}
    \right.
$$

We will also be assessing the results and performance of trading decisions, and the returns at time $t$ will be obtained using "ruled returns", which will be denoted as $R_t$.  So if for a period $[t-1, t)$, a trader establishes a  position at time $t-1$, represented by $B_{t-1}$, the "ruled returns" expression is as follows:

$$R_t = B_{t-1}X_t \iff \left\{
                            \begin{array}{ll}
                            R_t = -X_t & \quad  B_{t-1} = -1\\
                            R_t = +X_t & \quad  B_{t-1} = +1
                            \end{array}
                          \right.
$$

where $X_t = ln(P_t/P_{t-1})$ denote the logarithm return over this period (so we will be assuming no dividend payouts during the time period).

The realized returns will thus be determined using:
$$\tilde{R_t} = \sum_{D = 1}^{n}R_{t + D}$$

where $D$ represents the stochastic duration of the position lasting $n$ days provided that:

$$\left\{D = n\right\} \iff \left\{B_{t-1} \neq B_t, B_t = ... = B_{t+n-1}, B_{t+n-1} \neq B_{t+n}\right\}$$

###Step 1: Derive variance of predictor $F_t$
The variance of the predictor is derived as follows:

$$\sigma_F^2 = var(\sum_{i = 0}^{m-2} d_i X_{t-i})$$
$$= cov(\sum_{i = 0}^{m-2} d_iX_{t-i}, \sum_{i = 0}^{m-2}d_iX_{t-i})$$
$$= d_0cov(X_t, \sum_{i = 0}^{m-2}d_iX_{t-i}) + d_1cov(X_{t-1}, \sum_{i = 0}^{m-2}d_iX_{t-i}) + ... + d_{m-2}cov(X_{t-m+2}, \sum_{i = 0}^{m-2}d_iX_{t-i})$$
$$= d_0(d_0\gamma_0 + d_1\gamma_1 + ... + d_{m-2}\gamma_{m-2}) + d_1(d_0\gamma_1 + d_1\gamma_0 + d_2\gamma_1 + ... + d_{m-2}\gamma_{m-3}) + ... + d_{m-2}(d_0\gamma_{m-2} + d_1\gamma_{m-3} + ... + d_{m-2}\gamma_0)$$
$$= \gamma_0 \sum_{i = 0}^{m-2}d_i^2  + 2\sum_{i = 1}^{m-2} \sum_{j = 0}^{m-2-i}d_jd_{j+i}\gamma_i$$
$$= \gamma_0 (\sum_{i = 0}^{m-2}d_i^2  + 2\sum_{i = 1}^{m-2} \sum_{j = 0}^{m-2-i}d_jd_{j+i}\rho_i)$$
$$= \gamma_0 (\sum_{i = 0}^{m-2}d_i^2  + 2\sum_{j = 0}^{m-2} \sum_{i = j+1}^{m-3}d_jd_{i}\rho_{i-j})$$

Provided below is the R code for computing the variance of the predictor:

```{r results = "hide"}
#Step 1: Get the variance of the predictor
# d: vector of dj coefficients (j = 0, ..., m-2)
# X: log returns
#Will use quadratic form... 
varF <- function(d, X){
	#maximum lag
	M <- length(d)-1
	#get auto-covariance
	acfs <- acf(X, plot = F, type="covariance", lag.max=M)$acf
	#get toeplitz matrix of acfs
	#name used to refer to:
	#[[\gamma_0, ..., \gamma_{m-2}],
	# [\gamma_1, \gamma_0, ..., \gamma_{m-3}], ...
	# [\gamma_{m-2}, ..., \gamma_0]]
	Gamma <- toeplitz(as.vector(acfs))
	#quadratic form
	varF <- d%*%Gamma%*%as.vector(d)
	varF
}

```

Note that the implementation above uses the quadratic form of the expression:

$$\sigma_F^2 =
\left[\begin{array}{ccc}
        d_0 & ... & d_{m-2}
        \end{array}\right]
\left[\begin{array}{ccc}
        \gamma_0 & ... & \gamma_{m-2}\\
        ... & ... & ...\\
        \gamma_{m-2} & ... & \gamma_{0}
        \end{array}\right]
\left[\begin{array}{c}
        d_0\\
        ...\\
        d_{m-2}
      \end{array}\right]
$$

###Step 2: Derive expectation of predictor $F_t$
The expectation of the predictor is derived as follows:

$$\mu_F = E(\sum_{i=0}^{m-2} d_iX_{t-i})$$
$$= \sum_{i=0}^{m-2} d_iE(X_{t-i})$$
$$= \mu_X\sum_{i=0}^{m-2} d_i$$

Provided below is the R code for computing the expectation of the predictor:

```{r results = "hide"}
#Step 2: Get the expectation of the predictor
# d: vector of dj coefficients (j = 0, ..., m-2)
# X: log returns
muF <- function(d, X){
	muF <- mean(X)*sum(d)
	muF
}

```

###Step 3: Derive autocorrelation function at lag one for predictor
The expression for the autocorrelation function for lag 1 is derived as follows:

$$\rho_F(1) = corr(F_t, F_{t - 1}) = \frac{cov(F_t, F_{t - 1})}{var(F_t)}$$

First the covariance expression,

$$cov(F_t, F_{t - 1})= corr(\sum_{i=0}^{m-2} d_iX_{t-i}, \sum_{i=0}^{m-2} d_iX_{t-1-i})$$
$$= d_0cov(X_t, \sum_{i=0}^{m-2} d_iX_{t-1-i}) + d_1cov(X_{t-1}, \sum_{i=0}^{m-2} d_iX_{t-1-i}) + ... + d_{m-2}cov(X_{t-m+2}, \sum_{i=0}^{m-2} d_iX_{t-1-i})$$
$$= d_0(d_0\gamma_1 + d_1\gamma_2 + ... + d_{m-2}\gamma_{m-1}) + d_1(d_0\gamma_0 + d_1\gamma_1 + d_2\gamma_2 + ... + d_{m-2}\gamma_{m-2}) + ... + d_{m-2}(d_0\gamma_{m-3} + d_1\gamma_{m-4} + ... + d_{m-2}\gamma_1)$$
$$= \gamma_0\left\{ d_0(d_0\rho_1 + d_1\rho_2 + ... + d_{m-2}\rho_{m-1}) +  ... + d_{m-2}(d_0\rho_{m-3} + d_1\rho_{m-4} + ... + d_{m-2}\rho_1) \right\}$$
$$= \gamma_0\sum_{i = 0}^{m-2}\sum_{j = 0}^{m-2}d_id_j\rho_{j - 1 - i}$$

Then the autocorrelation function:

$$\rho_F(1) = \frac{cov(F_t, F_{t - 1})}{var(F_t)}$$
$$= \frac{\gamma_0\sum_{i = 0}^{m-2}\sum_{j = 0}^{m-2}d_id_j\rho_{j - 1 - i}}{var(F_t)}$$

Provided below is the R code for computing the lag one autocorrelation of the predictor:

```{r results = "hide"}
#Step 3: Computing ACF(1) of forecaster
#will use a quadratic form
# d: vector of dj coefficients (j = 0, ..., m-2)
# X: log returns
rhoF <- function(d, X){
	#max lag
	M <- length(d)-1
	#get acfs
	acfs <- acf(X, plot = F, type = "covariance", lag.max = M+2)$acf
	#get the covariance
	temp <- d%*%matrix(acfs[as.vector(
	abs(outer(0:M,1:(M+1), "-"))+1)], M+1, M+1)%*%as.vector(d)
	rhoF <- temp/varF(d, X)
	rhoF
}
```

Additionally note that as with when computing the variance of the predictor, a similar approach utilizing matrix multiplication is being used above:

$$cov(F_t, F_{t-1}) =
\left[\begin{array}{ccc}
        d_0 & ... & d_{m-2}
        \end{array}\right]
\left[\begin{array}{cccc}
        \gamma_1 & ... & ... &\gamma_{m-1}\\
        ... & ... & ...& ...\\
        ... & ... & ...& ...\\
        \gamma_{m-3} & ... & \gamma_0 & \gamma_1
        \end{array}\right]
\left[\begin{array}{c}
        d_0\\
        ...\\
        d_{m-2}
      \end{array}\right]
$$

###Step 4: Computing the expected ruled returns and expected holding period length

Under the assumption that $X_t$ follows a stationary Gaussian process, the expected ruled returns has been provided as follows:

$$E(R_t) = \sqrt{\frac{2}{\pi}}\sigma_Xcorr(X_t,F_{t-1})exp\left\{-\frac{\mu_F^2}{2\sigma_F^2}\right\} + \mu_X(1 - 2\phi\left[ -\frac{\mu_F}{\sigma_F} \right])$$

Most of the expressions needed for this computation has been derived earlier.  We just need the expression:

$$corr(X_t,F_{t-1}) = \frac{cov(X_t,F_{t-1})}{\sqrt{\gamma_0var(F_t)}}$$
$$= \frac{(d_0\gamma_1 + d_1\gamma_2 + ... + d_{m-2}\gamma_{m-1})}{\sqrt{\gamma_0var(F_t)}}$$
$$= \frac{\gamma_0\sum_{i=0}^{m-2}d_i\rho_{i+1}}{\sqrt{\gamma_0var(F_t)}}$$

The R code for implementing this computation is as follows:

```{r results = "hide"}
#Step 4 Intermediate: correlation between X_t and F_{t-1}
#will use a quadratic form
# d: vector of dj coefficients (j = 0, ..., m-2)
# X: log returns

corXF <- function(d, X){
	Mp <- length(d)
	acfs <- acf(X, plot = F, type = "covariance", lag.max = Mp)$acf
	corXF <- sum(d*acfs[-1])/sqrt(acfs[1]*varF(d, X))
	corXF
}
```

Additionally, the unconditional variance of the ruled returns has been provided as:

$$var(R_t) = E(X_t^2) - E(R_t)^2 = \sigma_X^2 + \mu_X^2 - E(R_t)^2$$

Furthermore, as provided, Kedem (1986) shows that the expected zero-crossing rate for a discrete-time, zero-mean, stationary Gaussian sequence $Z_t$ is given by:

$$\frac{1}{\pi}cos^{-1}\rho_Z(1)$$

where $\rho_Z(1)$ denotes the autocorrelation function of $\left\{Z_t\right\}$ at lag one.  Using this result, we may approximate the expected length of the holding period to be:

$$H = \frac{\pi}{cos^{-1}\rho_F(1)}$$

Provided below is the R code for the computation of the expected holding period, the double MA co-efficients and the expected ruled returns:

```{r results = "hide"}
#Step 4: Expected holding period and ruled returns
#expected holding period
#rho is lag one autocorrelation
#provided by step 3
Hold <- function(rho){
	Hold <- pi/acos(rho)
}

#next is the double MA co-efficients
d <- function(m, r){
	d <- c((m-r)*((0:(r-1))+1), r*(m-(r: (m-1))-1))
	d
}

# retX: log asset return
# m: long-term MA
# r: short-term MA

ruleReturn <- function(retX, m, r){
	#returns variance
	vX <- sd(retX)
	#returns mean
	mX <- mean(retX)
	#predictor mean
	mF <- muF(d(m, r), retX)
	#predictor sd
	vF <- sqrt(varF(d(m, r), retX))
	#lag 1 correlation (rho) between X_t and F_{t-1}
	rXF <- corXF(d(m, r), retX)
	#lag 1 correlation of predictor
	rF <- rhoF(d(m, r), retX)
	#expected return
	ER <- sqrt(2/pi)*vX*rXF*exp(-mF*mF/(vF*vF)) + 
	mX*(1-2*pnorm(-mF/vF))
	#expected hold duration
	H <- Hold(rF)
	#return results
	list("ER" = ER, "H" = H, "rhoF" = rF, "VF"= vF, "muF"=mF, 
	"corXF"=rXF)
}

```

###Step 5: Downloading the monthly data of the constituents
The data for the DJ constituents were downloaded from Yahoo Finance in csv files and stored in a folder.  The R code for retrieving this data from the csv files is as follows:

```{r results = "hide"}
#This function is to download data from folder...
#idea: return three arrays - one containing the stock tickers...
#	another the adjusted close (using hint from prev assn) 
#	and finally one containing the log returns

# dataDir: directory containing csv files containing data
# currDir: current working directory (to change back to after 
#	loading data)
getAdC <- function(dataDir, currDir){
	#switch to directory containing price data
	setwd(dataDir)
	#get list of files in directory
	priceFiles <- list.files(dataDir, pattern="*.csv", 
	full.names = F, recursive = F)
	#to hold tickers
	tickers <- c()
	#to hold prices
	prices <- c()
	#to hold log returns
	logrets <- c()
	#iterate through list above
	for (file in seq(1, length(priceFiles))){
		tickers <- c(tickers, substr(priceFiles[file],
		1,nchar(priceFiles[file])-4))
		#use rbind for the adjusted close data...
		#first read the file
		stockdat <- read.csv(file = priceFiles[file],
		 header = T, sep=",")
		#then get adjusted close prices from file
		price <- stockdat[1:dim(stockdat)[1], 6] 
		prices <- rbind(prices, price)
		#also the log returns
		logrets <- rbind(logrets, 
		log(price[2:length(price)]/price[1:(length(price)-1)]))
	}
	#return to original directory
	setwd(currDir)
	
	#return tickers, prices and log returns
	list("tickers"=tickers, "prices"=prices, "logrets" = logrets)
}

```

###Step 6: Writing R function to find optimal monthly double MA trading rules
Provided below are the R functions utilized to find the optimal double MA trading rules using monthly data:

```{r results = "hide"}
#Function to choose the optimal daily and monthly MA trading rules
#	(i.e. that maximize expected rule returns)
#will test function against the one in prev assn after 
#	implementation...

#first optimal monthly
#	retX: vector of log returns
monthlyoptimal_dma <- function(retX){
	#to hold optimal m and r
	optimal_m <- 2
	optimal_r <- 1
	#get ruleReturn for this setting
	currER <- ruleReturn(retX, optimal_m, optimal_r)$ER
	#iterate up to 12 max as we are doing monthly
	#loop through r
	for (i in seq(1, 11)){
		for (j in seq(i+1, 12)){
			ERij <- ruleReturn(retX, j, i)$ER
			if (ERij > currER){
				optimal_m <- j
				optimal_r <- i
				currER <- ERij
			} 
		}
	}
	#return optimal double MA trading rules
	list("monthlyoptimal_m"=optimal_m, "monthlyoptimal_r"=optimal_r)
}

#functions that will implement the above for all constituents...

#	retsX: the log returns of the constituents 

monthlyoptimals_dma <- function(retsX){
	#to hold the optimal trading rules
	m <- c()
	r <- c()
	#amount of tickers to go through
	numstocks <- dim(retsX)[1]
	#number of periods/ months
	months <- dim(retsX)[2]
	for (i in seq(1, numstocks)){
		optimals <- monthlyoptimal_dma(retsX[i, 1:months])
		#add optimals to list
		m <- c(m, optimals$monthlyoptimal_m)
		r <- c(r, optimals$monthlyoptimal_r)
	} 
	
	#return optimal rules
	list("monthlyoptimals_m"=m, "monthlyoptimals_r"=r)
}
```

Disclosed below are the optimal trading rules found for the constituents:

```{r, echo=FALSE}
dataDir <- "/Users/amanull9/Documents/STA457/Assignments/Assn 1/DJ Data Monthly"
currDir <- "/Users/amanull9/Documents/STA457/Assignments/Assn 1"

monthlydata <- getAdC(dataDir, currDir)
tickers <- monthlydata$tickers
mprices <- monthlydata$prices
mlogrets <- monthlydata$logrets

#get optimals for all 30 constituents
dj_optimals <- monthlyoptimals_dma(mlogrets)

#construct table
djoptimals_table <- t(rbind(tickers, dj_optimals$monthlyoptimals_m,dj_optimals$monthlyoptimals_r))

#column names
colnames(djoptimals_table)[2:3] <- c("m", "r")

#kable
library(knitr)
kable(djoptimals_table, caption = "DJ double MA optimal trading rules")

```

###Step 7: Writing R function to compute in-sample trading statistics and compare with theoretical results

Please find below the functions implemented in R to generate the in-sample as well as theoretical trade statistics (cumulative return and holding time) for the optimal trade rules derived earlier.

```{r results = "hide"}
#functions for computing in-sample trading statistics 
#	(i.e. cumulative return and holding time)
#	to later compare with theoretical results
#first function to compute the predictor

#	d: d is d(m ,r) - presumably the optimal ones found
#	retX: the log returns
#	t: get signal at time t

f <- function(d, retX, t){
	M <- length(d) - 1
	if (t >= M){
		output <- sum(d*rev(retX[(t-M):t]))
		output
	}
	else {print('t is smaller than M')}
}

#next the realized return
#	d: d is d(m ,r) - presumably the optimal ones found
#	retX: the log returns
realized_ret <- function(d, retX){
	re <- c()
	M <- length(d)
	for (t in seq(M + 1,length(retX))){
		re <- c(re, sign(f(d, retX, t-1))*retX[t])
	}
	realized_ret <- sum(re)/length(M:length(retX))
	realized_ret
}

#next is the holding period
holding_period <- function(d, retX){
	num_change <- 0
	M <- length(d)
	for (t in seq(M+1, length(retX))){
		if (sign(f(d, retX,t)) != sign(f(d, retX,t-1))){
			num_change <- num_change + 1
		}
	}
	hold <- length(M:length(retX))/num_change
	hold
}

#function that will take in the array of log returns 
#	and the optimal trading decisions
in_sample_estimate <- function(retX, m, r){
	#number of tickers
	num_stocks <- dim(retX)[1]
	#number of periods/ months
	#to hold in_sample and theoretical values
	djER <- c()
	djH <- c()
	djISR <- c()
	djISH <- c()
	months <- dim(retX)[2]
	for (i in seq(1, num_stocks)){
		ruleReturn_i <- ruleReturn(retX[i, 1:months], m[i], r[i])
		djER <- c(djER, ruleReturn_i$ER)
		djH <- c(djH, ruleReturn_i$H)
		djISR <- c(djISR, 
		realized_ret(d(m[i],r[i]),retX[i, 1:months]))
		djISH <- c(djISH, 
		holding_period(d(m[i],r[i]),retX[i, 1:months]))
	}
	#return estimated and theoretical values 
	list("djER"=djER ,"djH"=djH, "djISR"=djISR, "djISH"=djISH)
}

```

The results are disclosed below as well:
```{r, echo=FALSE}
dj_tradestats <- in_sample_estimate(mlogrets,dj_optimals$monthlyoptimals_m,dj_optimals$monthlyoptimals_r)

#Ok outputting something which is good

#code for having this in a table
dj_tradestats_table <- t(rbind(tickers, round(dj_tradestats$djER,4),  round(dj_tradestats$djISR,4), round(dj_tradestats$djH,3), round(dj_tradestats$djISH,3)))

colnames(dj_tradestats_table)[2:5] <- c("theoretical return",  "expected return","theoretical hold", "expected hold")

#kable
kable(dj_tradestats_table, caption = "DJ double MA optimal trading rules statistics")

```

## Question 2
In this section, we will construct the equally weighted (EW) and risk-parity (RP) weighted portfolios using the 30 DJ constituents and summarize the performance.  

As per general instruction, performance will be based on a 60-month rolling window and the portfolio will be rebalanced monthly.  The parameters ($\sigma$) will be calibrated/ estimated at the end of each year.

The following assumptions are going to be made:

  1. Will use the 60-month window to get optimal trading rules
  
  2. Will use these optimal settings to predict the signals for next month
  
  3. For risk parity, will use the last 261 days of window to calibrate the asset volatilities (see section B) as brought up earlier.
  
  4. Use predicted signal and portfolio weights to get rule return of portfolio (see hint).
  
  5. Check performance of next 12 months.  Will rebalance portfolio in each of these 12 months (so only risk parity will have altered distributions).
  
  6. The 60-month window moves 12 months ahead and we repeat (1-5).  Process terminates when we reach the end of our data.
  
Please find the implementation of these steps for the equally weighted portfolio as follows:

```{r results = "hide"}
#Question 2: summarizing performance of the equally weighted
#	portfolio
#	retX: 30X(periods) dim matrix of log returns

ew_performance <- function(retX){
	#number of stocks provided
	num_stocks <- dim(retX)[1]
	#number of periods of data provided
	months <- dim(retX)[2]
	#to hold the ruled returns
	re <- c()
	#only go up to as long as window can be fit
	for (i in seq(1, months - 60, 12)){
		#get optimal dma within 60 month window for all stocks
		optimal_dma <- monthlyoptimals_dma(
		retX[1:num_stocks, i:(i+60-1)])
		m <- optimal_dma$monthlyoptimals_m
		r <- optimal_dma$monthlyoptimals_r
		#Ok, now use this to get ruled returns for the 12 months
		#	after this rolling window
		#we will iterate through the 12 months following this window
		#	and iterate through the stocks
		for (t in seq(i + 60, i + 72 -1)){
			if (t <= months){
				re_t <- 0
				for (s in seq(1, num_stocks)){
					s_d <- d(m[s], r[s])
					re_t <- re_t + (1/num_stocks)*
					sign(f(s_d, retX[s, 1:months], t-1))*retX[s,t]
				}
				#now add the portfolio ruled return
				re <- c(re, re_t)
				#note that since this is a EW portfolio, there is 
				#	no rebalancing step as weights remain the same 
			}
		}
	}
	#the above will give me the ruled returns - can use this to
	#	get realized return...
	#note that annualized expected return, volatility and sharpe
	#	ratio are needed
	#we can get the monthly expected return as follows:
	realized_ret <- sum(re)/length(re)
	#can convert this to annual as follows:
	realized_ret <- 12*realized_ret
	#question is though how I get the annualized volatility?
	#do I just get the volatility of the assets from the returns
	#	data and then just sum (1/30)^2*volatility, then annualize?
	#do this for now...
	volatility <- 0
	for (s in seq(1, num_stocks)){
		volatility <- volatility + (1/30)^2*(sd(retX[s, 1:months]))^2
	}
	#convert to annualized
	volatility <- sqrt(12)*sqrt(volatility)
	#next is annualized sharpe ratio
	#assuming 0.02 annual-risk free for this assn
	sharpe <- (realized_ret - 0.02)/volatility
	#return results
	list("return"=realized_ret, "volatility"=volatility,
	 "sharpe"=sharpe)
}
```

The performance results obtained implementing the function above is as follows:

```{r, echo=FALSE}

#dj_ew_performance <- ew_performance(mlogrets)

#Ok outputting something which is good

#code for having this in a table
#dj_ew_performance_table <- t(rbind(round(dj_ew_performance$return,4),  round(dj_ew_performance$volatility,4), round(dj_ew_performance$sharpe,4)))

#colnames(dj_ew_performance_table)[1:3] <- c("Annualized expected return",  "Annualized volatility","Annualized sharpe ratio")

#kable
#kable(dj_ew_performance_table, caption = "EW performance metrics")

```

# Part B
## Question 1
In this section, we will cover the computation of the ex-ante volatility estimate $\sigma_t$ for the DJ constituents.  The formula used is:

$$\sigma_{s,t}^2 = 261\sum_{i = 0}^{260}(1-\delta)\delta^i(r_{s,t-1-i}-\bar{r}_{s,t})^2$$

Where the weights $\delta^i(1-\delta)$ add up to one, and $\bar{r}_{s,t}$ is the exponentially weighted average return computed similarly:

$$\bar{r}_{s,t} = \sum_{i = 0}^{260}(1-\delta)\delta^ir_{s,t-1-i}$$

So, first let's try to solve for $\delta$. We will retrieve the $\delta$ value using the same reasoning as Moskowitz in his journal, i.e. choose $\delta$ so that the centre of mass of the weights is:

$$\sum_{i = 0}^{\infty} (1-\delta)\delta^ii = \frac{\delta}{1-\delta} = 60 days$$
$$\delta = 60(1-\delta)$$
$$61\delta = 60$$
$$\delta = \frac{60}{61} = ~0.9836$$


